---
title: "Test"
author: "Christina Lim"
date: "3/10/2022"
output:
  pdf_document: default
  html_document: default
---
```{r}
library(tinytex)
```


```{r}
vax <- read.csv("covid19vaccinesbyzipcode_test.csv")
head(vax,3)
```

```{r}
head(vax$persons_fully_vaccinated)
```
```{r}
nrow(vax)
```
#What is the latest date in this dataset?
```{r}
vax$as_of_date[nrow(vax)]
```
#install.packages("lubridate)
```{r}
library(lubridate)
```
```{r}
today()
```
```{r}
vax$as_of_date[1]
```

```{r}
vax$as_of_date <- ymd(vax$as_of_date)
today() - vax$as_of_date[1]
```
```{r}
today() - vax$as_of_date[nrow(vax)]
```
```{r}
vax$as_of_date[nrow(vax)] - vax$as_of_date[1]
```
```{r}
length(unique((vax$zip_code_tabulation_area)))
```
```{r}
time_length(today()-ymd("1996-08-29"),"years")
```
#Convert(overwrite) the `as of date` column by the output of `ymd()` function
```{r}
#specify that we are using year-month-date format. 

vax$as_of_date <- ymd(vax$as_of_date)
```

#Now we can take the last date and subtract the first date recorded to find the time spent in this dataset
```{r}
today() - vax$as_of_date[1]
```

#Now we focus on San Diego

```{r}
sd <- vax[vax$county == "San Diego",]
```
#We need dplyr

#install.packages("tidyverse", dependencies = TRUE)
```{r}
library(tidyverse)
```
Using the filter dplyr way 
```{r}
sd <- filter (vax, county == "San Diego")
head(sd,3)
```
#How many unique zipcodes in San Diego county?

```{r}
length(unique((vax$zip_code_tabulation_area)))
```

#Or another way:
```{r}
#install.packages("zipcodeR")
library(zipcodeR)
```
```{r}
geocode_zip('92037')
```
```{r}
x <- c(10,9,8,20)

inds <- order (x, decreasing = TRUE)
x[inds]
```

```{r}
inds <- order(sd$age12_plus_population, decreasing = TRUE)
sd[inds[1],]
```
#Or another way:

```{r}
ind <- which.max(sd$age12_plus_population)
sd$zip_code_tabulation_area[ind]
```

#Using dplyr:

```{r}
arrange(sd, -age12_plus_population) %>%
select(zip_code_tabulation_area)
```
```{r}
library(ggplot2)
```

```{r}
lj <- filter(vax, zip_code_tabulation_area == "92037")
ggplot(lj) + 
  aes(x = as_of_date, 
      y = percent_of_population_fully_vaccinated) + 
  geom_point() + geom_line(group=1) + ylim(c(0,1)) +
  labs(x= "Date", y = "Percent Vaccinated")
```
```{r}
lj <- filter(sd, as_of_date == "2022-03-01")
sd.ave <- mean(lj$percent_of_population_fully_vaccinated, na.rm = TRUE)
sd.ave
```

#Or 

```{r}
sd %>% filter (as_of_date == "2022-03-01") %>%
  select(percent_of_population_fully_vaccinated) %>%
  colMeans(na.rm=T)
```

#histogram:

```{r}
sd.today <- filter(sd, as_of_date == "2022-02-22")
summary(sd.today$percent_of_population_fully_vaccinated)
```
```{r}
hist(sd.today$percent_of_population_fully_vaccinated)
```
#OR

```{r}
ggplot(sd.today) + 
  aes(percent_of_population_fully_vaccinated) + 
  geom_histogram() + 
  geom_rug()
```
#What is the age 5+ population of 92037 area?

```{r}
ucsd <- filter(sd, zip_code_tabulation_area == "92037")
ucsd[1,]$age5_plus_population
```

```{r}
filter(vax, zip_code_tabulation_area =="92037") %>%
         ggplot() + 
         aes (as_of_date, percent_of_population_fully_vaccinated)+
         geom_point()+
         geom_line()+
         geom_hline(yintercept = sd.ave, col = "red", linetype=2)
```
We want a time-course plot of all zipcode areas with a population as large as CA 92037
```{r}
vax.36.all <- filter(vax, age5_plus_population > 36144)

ggplot(vax.36.all) +
  aes(as_of_date, 
      percent_of_population_fully_vaccinated,
      group = zip_code_tabulation_area) +
  geom_line(col = "blue")

```

